Sampling Strategies in Decisions from Experience

### 2022-05-17 manuscript.Rmd
Figures via latex expressions

authornote: |
 This manuscript is a dynamic document which can be reproduced using the materials and instructions provided on the `GitHub repository`: https://github.com/linushof/sampling-in-dfe. The current version of the manuscript, created from the commit with the `hash `r repro::current_hash()``, is prepared for submission as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology. Supervisors:

@@

(ref:weighting-function) Possible Graphical Shapes of Goldstein and Einhorn's -@goldsteinExpressionTheoryPreference1987 Weighting Function

```{r weighting-function, fig.cap="(ref:weighting-function)"}
#compute images of weighting function (wf)
wf <- tibble(p = seq(0, 1, .01)) %>%  #cumulative probabilities
  expand_grid(gamma = seq(.1, 2, .1), #gamma values
              delta = c(.1, .5, 1, 2, 5, 10)) %>% #delta values
  mutate(wp = (delta*(p^gamma))/((delta*p^gamma)+(1-p)^gamma)) #images of wf

@@

@@

(ref:chain-length) Lengths of Information-Processing Chains

```{r fig.cap="(ref:chain-length)", eval = FALSE}
chain_lengths <- choices_absolute %>%
  ggplot(aes(x = s, y = n_sample, color = model)) +
  facet_wrap(~a, nrow = 2, scales = "free") + 
  labs(x = expression(psi),
       y = "Number of Sampled Outcomes",
       color = "Model") + 
  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5))+
  geom_jitter(alpha = .05) + 
  geom_smooth(color = "gray") + 
  geom_hline(yintercept = 14, linetype = "dashed", color = "gray") +
  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  theme_minimal()
chain_lengths
```

```{r chain-length, fig.cap="(ref:chain-length)", out.width="100%"}
knitr::include_graphics(path = "manuscript_files/chain-lengths.png")
```

@@

(ref:choice-rates-roundwise) Rates of False Risky and False Safe Choices in the Round-Wise Integration Model

```{r choice-rates-roundwise, fig.cap="(ref:choice-rates-roundwise)"}
#prepare data

@@

(ref:choice-rates-summary) Rates of False Risky and False Safe Choices in the Summary Integration Model

```{r choice-rates-summary, fig.cap="(ref:choice-rates-summary)"}
#prepare data

@@

@@

(ref:weighting-parameters) Parameter Estimates of the Weighting Function

```{r weighting-parameters, fig.cap="(ref:weighting-parameters)"}

@@

@@

(ref:sensitivity-parameters) Parameter Estimates of the Outcome and Choice Sensitivity Parameter

```{r sensitivity-parameters, fig.cap="(ref:sensitivity-parameters)"}

@@

@@

(ref:function-forms) Estimated Graphical Shape of the Weighting and Value Function

```{r function-forms, fig.cap="(ref:function-forms)"}

@@

>>>>

authornote: |
 This manuscript is a dynamic document which can be reproduced using the materials and instructions provided on the `GitHub` repository: https://github.com/linushof/sampling-in-dfe. The current version of the manuscript, created from the commit with the hash ``r repro::current_hash()``, is submitted as a master's thesis in fulfillment of the requirements for the degree Master of Science (M.Sc.) at Heidelberg University, Faculty of Behavioural and Cultural Studies, Institute of Psychology. Supervisors:

@@

```{r weighting-function, include=FALSE}
#compute images of weighting function (wf)
wf <- tibble(p = seq(0, 1, .01)) %>%  #cumulative probabilities
  expand_grid(gamma = seq(.1, 2, .1), #gamma values
              delta = c(.1, .5, 1, 2, 5, 10)) %>% #delta values
  mutate(wp = (delta*(p^gamma))/((delta*p^gamma)+(1-p)^gamma)) #images of wf

@@

\begin{figure}[t]
\caption{Possible Graphical Shapes of Goldstein and Einhorn's (\protect\hyperlink{ref-goldsteinExpressionTheoryPreference1987}{1987}) Weighting Function}
\includegraphics{manuscript_files/figure-latex/weighting-function-1} \label{fig:weighting-function}
\raggedright \textit{Note.} Add note
\end{figure}

@@

```{r chain-length, eval = FALSE}
chain_lengths <- choices_absolute %>%
  ggplot(aes(x = s, y = n_sample, color = model)) +
  facet_wrap(~a, nrow = 2, scales = "free") + 
  labs(x = expression(psi),
       y = "Number of Sampled Outcomes",
       color = "Model") + 
  scale_x_continuous(limits = c(0,1), breaks = seq(0,1,.5))+
  geom_jitter(alpha = .05) + 
  geom_smooth(color = "gray") + 
  geom_hline(yintercept = 14, linetype = "dashed", color = "gray") +
  scale_color_manual(values = c("#35b779" ,"#3e4989")) + 
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  theme_minimal()
chain_lengths
```

\begin{figure}[t]
\caption{Lengths of Information-Processing Chains}
\includegraphics[width=1\linewidth]{manuscript_files/chain-length} \label{fig:chain-length}
\raggedright \textit{Note.} Add note
\end{figure}

@@

```{r choice-rates-roundwise, include=FALSE}
#prepare data

@@

\begin{figure}[t]
\caption{Rates of False Risky and False Safe Choices in the Round-Wise Integration Model}
\includegraphics{manuscript_files/figure-latex/choice-rates-roundwise-1} \label{fig:choice-rates-roundwise}
\raggedright \textit{Note.} Add note
\end{figure}

```{r choice-rates-summary, include=FALSE}
#prepare data

@@

\begin{figure}[t]
\caption{Rates of False Risky and False Safe Choices in the Summary Integration Model}
\includegraphics{manuscript_files/figure-latex/choice-rates-summary-1} \label{fig:choice-rates-summary}
\raggedright \textit{Note.} Add note
\end{figure}

@@

```{r weighting-parameters, include=FALSE}

@@

\begin{figure}[t]
\caption{Parameter Estimates of the Weighting Function}
\includegraphics{manuscript_files/figure-latex/weighting-parameters-1} \label{fig:weighting-parameters}
\raggedright \textit{Note.} Add note
\end{figure}

@@

```{r sensitivity-parameters, include=FALSE}

@@

\begin{figure}[t]
\caption{Parameter Estimates of the Outcome and Choice Sensitivity Parameter}
\includegraphics{manuscript_files/figure-latex/sensitivity-parameters-1} \label{fig:sensitivity-parameters}
\raggedright \textit{Note.} Add note
\end{figure}

@@

```{r function-forms, include=FALSE}

@@

\begin{figure}[t]
\caption{Estimated Graphical Shape of the Weighting and Value Function}
\includegraphics{manuscript_files/figure-latex/function-forms-1} \label{fig:function-forms}
\raggedright \textit{Note.} Add note
\end{figure}
